Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-13 prop_letter.tex
prop_letter.tex C(\bar{μ}, S) reorganizing...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability using a probability measure
$\mu : P \rightarrow [0,1]$ to a probability $\mu(P_{i})$. We impose
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
measures obey
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with the
measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199}.
$\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

@@

For example, assuming the three intervals $\imposs=\left[0,0\right]$,
$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in
question; any quantum state would be consistent with $\bar{\mu}_{1}$
on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ to
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents the situation in which that an experimenter knows nothing about a
coin before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation for which an experimenter
has no prior knowledge.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fuzzy Measurements}
 \label{sec:fuzzy}
A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the quantum case, the
events of interest are specified by \emph{projection operators}
$P$. These include the empty projection\nb$\mathbb{0}$, the identity
projection\nb$\mathbb{1}$, projections of the form $\proj{\psi}$ where
$\ket{\psi}$ is a pure quantum state (an element of a Hilbert space),
sums of \emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using
a probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projections on a given Hilbert space. We impose
the following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, standard probability
measures obey
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with the
measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\citep{Born1983,peres1995quantum,544199}. Given a set
of projectors\nb$S$, 
\begin{equation}
\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{mixed state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
\end{equation}
is the set of all mixed states consistent with $\bar{\mu}$ on every
projector in $S$. For example, assuming the three intervals $\imposs=\left[0,0\right]$,
$\necess=\left[1,1\right]$, and $\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question;
any quantum state would be consistent with $\bar{\mu}_{1}$ on any
projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is
just the set of all mixed states.

@@

For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Consider $\bar{\mu}_{1}$ defined
in the previous paragraph. Restricting $\bar{\mu}_{1}$ to
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents the situation in which that an experimenter knows nothing about a
coin before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation for which an experimenter
has no prior knowledge.
